---
output:
  pdf_document:
    latex_engine: lualatex
    pandoc_args: "--pdf-engine-opt=-shell-escape"
    keep_tex: true
    toc: false
    toc_depth: 1
header-includes:
- '\usepackage{fontawesome,parskip,ragged2e,array,longtable,enumitem,setspace,atbegshi,tabularx}'
- '\usepackage[skins]{tcolorbox}'
- '\newcolumntype{P}[1]{>{\justifying\arraybackslash}p{#1}}'
- '\usepackage[colorlinks=true,urlcolor=blue]{hyperref}'
- '\setmainfont{Roboto}'
- '\definecolor{accent}{RGB}{31,56,100}'
- '\definecolor{lightbg}{RGB}{245,247,250}'
- '\definecolor{chipbg}{RGB}{220,228,240}'
geometry: "left=15mm,right=15mm,top=5mm,bottom=0mm"
---

```{r setup,include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
# directory<-paste0(dirname(rstudioapi::getActiveDocumentContext()$path),"/")
directory <- paste0(getwd(), "/")
df_work        <- openxlsx::read.xlsx(paste0(directory, "cv.xlsx"), sheet = "work")
df_education   <- openxlsx::read.xlsx(paste0(directory, "cv.xlsx"), sheet = "education")
df_examples    <- openxlsx::read.xlsx(paste0(directory, "cv.xlsx"), sheet = "examples")
df_details     <- openxlsx::read.xlsx(paste0(directory, "cv.xlsx"), sheet = "details")
df_description <- openxlsx::read.xlsx(paste0(directory, "cv.xlsx"), sheet = "description")
```

\tcbset{
  sectionbox/.style={
    enhanced,
    colback=lightbg,
    colframe=accent,
    colbacktitle=accent,
    coltitle=white,
    fonttitle=\bfseries,
    titlerule=0pt,
    arc=2pt,
    outer arc=2pt,
    top=6pt, bottom=6pt, left=8pt, right=8pt,
    toptitle=5pt, bottomtitle=5pt,
  }
}

\newtcbox{\skillchip}{
  nobeforeafter,
  colframe=accent!40,
  colback=chipbg,
  boxrule=0.4pt,
  arc=3pt,
  boxsep=0pt,
  left=1pt, right=1pt, top=2pt, bottom=2pt,
  tcbox raise base,
  fontupper=\small,
}

\thispagestyle{empty}

\begin{tcolorbox}[sectionbox, title=Dimitrios Zacharatos]
\begin{tabularx}{\linewidth}{@{}X r@{}}
```{r details,results='asis',echo=FALSE}
cat(paste0("\\small ", df_description$description[1], " &\n"))
cat("\\begin{tabular}[t]{@{}c@{\\,}l@{}}\n")
for (i in 1:nrow(df_details)) {
  icon <- sub("\\\\+$", "", df_details$icon[i])
  cat(paste0("  \\textcolor{accent}{", icon, "} & \\href{",
             df_details$link[i], "}{\\small ", df_details$label[i], "}\\\\\n"))
}
cat("\\end{tabular}\n")
```
\end{tabularx}
\end{tcolorbox}

\begin{tcolorbox}[sectionbox, title=Experience]
```{r work_experience,results='asis',echo=FALSE}
cat("\\begin{itemize}[leftmargin=0pt, label={}, itemsep=0.5em, topsep=0pt]\n")
for (i in 1:nrow(df_work)) {
  resp <- gsub("\\\\", " ", df_work[i, "responsibilities"], fixed = TRUE)
  cat("\\item\\begin{tabularx}{\\linewidth}{@{}p{2.6cm} X@{}}\n")
  cat(paste0("  \\textbf{\\textcolor{accent}{", df_work[i, "date_start"], "--",
             df_work[i, "date_finish"], "}} &\n"))
  cat(paste0("  \\textbf{", df_work[i, "company"], "} \\textbullet\\ ",
             df_work[i, "role"], " \\textit{\\small(", df_work[i, "status"], ")}\\\\\n"))
  cat(paste0("  & \\small ", resp, "\n"))
  cat("\\end{tabularx}\n")
}
cat("\\end{itemize}\n")
```
\end{tcolorbox}

\begin{tcolorbox}[sectionbox, title=Education]
```{r education,results='asis',echo=FALSE}
cat("\\begin{itemize}[leftmargin=0pt, label={}, itemsep=0.5em, topsep=0pt]\n")
for (i in 1:nrow(df_education)) {
  cat("\\item\\begin{tabularx}{\\linewidth}{@{}p{2.6cm} X@{}}\n")
  cat(paste0("  \\textbf{\\textcolor{accent}{", df_education[i, "date_start"], "--",
             df_education[i, "date_finish"], "}} &\n"))
  cat(paste0("  \\textbf{", df_education[i, "institution"], "}\\\\\n"))
  cat(paste0("  & \\small ", df_education[i, "qualification"], "\n"))
  cat("\\end{tabularx}\n")
}
cat("\\end{itemize}\n")
```
\end{tcolorbox}

\begin{tcolorbox}[sectionbox, title={Skills \normalfont\small(These are hyperlinks working in pdf)}]
```{r skills,results='asis',echo=FALSE}
for (cat_name in unique(df_examples$Experience)) {
  cat(paste0("\\textbf{\\textcolor{accent}{", cat_name, "}}\\\\[4pt]\n"))
  cat("\\raggedright\n")
  rows <- df_examples[df_examples$Experience %in% cat_name, ]
  for (j in seq_len(nrow(rows))) {
    cat(paste0("\\skillchip{\\href{", rows$link[j], "}{",
               rows$full_name[j], " (", rows$abbreviation[j], ")}} \\hspace{2pt}\n"))
  }
  cat("\n\\vspace{8pt}\n\n")
}
```
\end{tcolorbox}
